Gaps in stellar streams as a result of globular cluster fly-bys

### 2025-01-27 paper/main.tex
subhalos->sub-halos

  \citet{2017MNRAS.470...60E} concluded that the observed density variations in the tails of Palomar~5 could not be attributed to the passage of globular clusters. Their analysis focused on the characteristics of the observed gaps and involved constraining properties of the progenitor using reconstructive modeling. By trial and error, they identified a specific configuration of masses, sizes, impact parameters, times of impact, and relative velocities for two perturbers that successfully reproduced the observed density distribution. However, their method does not perform full forward modeling of the entire globular cluster system on Palomar5's stream, as we do in this work. While they suggest that the impact rate of globular clusters is likely less significant—given their lower abundance compared to the expected population of dark matter subhalos—they do not explore this aspect in detail. However, they do state that it is indeed an avenue for future investigation.

>>>>

  \citet{2017MNRAS.470...60E} concluded that the observed density variations in the tails of Palomar~5 could not be attributed to the passage of globular clusters. Their analysis focused on the characteristics of the observed gaps and involved constraining properties of the progenitor using reconstructive modeling. By trial and error, they identified a specific configuration of masses, sizes, impact parameters, times of impact, and relative velocities for two perturbers that successfully reproduced the observed density distribution. However, their method does not perform full forward modeling of the entire globular cluster system on Palomar~5's stream, as we do in this work. While they suggest that the impact rate of globular clusters is likely less significant—given their lower abundance compared to the expected population of dark matter sub-halos—-they do not explore this aspect in detail. However, they do state that it is indeed an avenue for future investigation.
